EldersAIR initial med visit data work

### 2021-03-11 elders_health_data_cleaning.Rmd
data cleaning, merging cleaned datasets

# Load and merge files from different locations
```{r}
nn_athomelog_initial <- read_xlsx(paste0(file_path, "Input/NN/athomelog.xlsx"),
                                   na = "NULL") %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         adult_id_num = as.character(AdultID),
         area = "NN",
         sampling_visit = as.numeric(SamplingVisit),
         at_home_day = as.factor(Day),
         "at_home_00:00:00" = as.factor("Yes"),
         "at_home_01:00:00" = as.factor("Yes"),
         "at_home_02:00:00" = as.factor("Yes"),
         "at_home_03:00:00" = as.factor("Yes"),
         "at_home_04:00:00" = as.factor("Yes"),
         "at_home_05:00:00" = as.factor("Yes"),
         "at_home_06:00:00" = as.factor("Yes"),
         "at_home_07:00:00" = as.factor(AtHome1),
         "at_home_08:00:00" = as.factor(AtHome2),
         "at_home_09:00:00" = as.factor(AtHome3),
         "at_home_10:00:00" = as.factor(AtHome4),
         "at_home_11:00:00" = as.factor(AtHome5),
         "at_home_12:00:00" = as.factor(AtHome6),
         "at_home_13:00:00" = as.factor(AtHome7),
         "at_home_14:00:00" = as.factor(AtHome8),
         "at_home_15:00:00" = as.factor(AtHome9),
         "at_home_16:00:00" = as.factor(AtHome10),
         "at_home_17:00:00" = as.factor(AtHome11),
         "at_home_18:00:00" = as.factor(AtHome12),
         "at_home_19:00:00" = as.factor(AtHome13),
         "at_home_20:00:00" = as.factor(AtHome14),
         "at_home_21:00:00" = as.factor(AtHome15),
         "at_home_22:00:00" = as.factor(AtHome16),
         "at_home_23:00:00" = as.factor("Yes")) %>% 
  select(home_winter_id:"at_home_23:00:00")

npt_athomelog_initial <- read_xlsx(paste0(file_path, "Input/NP/athomelog.xlsx"),
                                   na = "NULL") %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         adult_id_num = as.character(AdultID),
         area = "NPT",
         sampling_visit = as.numeric(SamplingVisit),
         at_home_day = as.factor(Day),
         "at_home_00:00:00" = as.factor("Yes"),
         "at_home_01:00:00" = as.factor("Yes"),
         "at_home_02:00:00" = as.factor("Yes"),
         "at_home_03:00:00" = as.factor("Yes"),
         "at_home_04:00:00" = as.factor("Yes"),
         "at_home_05:00:00" = as.factor("Yes"),
         "at_home_06:00:00" = as.factor("Yes"),
         "at_home_07:00:00" = as.factor(AtHome1),
         "at_home_08:00:00" = as.factor(AtHome2),
         "at_home_09:00:00" = as.factor(AtHome3),
         "at_home_10:00:00" = as.factor(AtHome4),
         "at_home_11:00:00" = as.factor(AtHome5),
         "at_home_12:00:00" = as.factor(AtHome6),
         "at_home_13:00:00" = as.factor(AtHome7),
         "at_home_14:00:00" = as.factor(AtHome8),
         "at_home_15:00:00" = as.factor(AtHome9),
         "at_home_16:00:00" = as.factor(AtHome10),
         "at_home_17:00:00" = as.factor(AtHome11),
         "at_home_18:00:00" = as.factor(AtHome12),
         "at_home_19:00:00" = as.factor(AtHome13),
         "at_home_20:00:00" = as.factor(AtHome14),
         "at_home_21:00:00" = as.factor(AtHome15),
         "at_home_22:00:00" = as.factor(AtHome16),
         "at_home_23:00:00" = as.factor("Yes")) %>% 
  select(home_winter_id:"at_home_23:00:00")

@@

# Combine logs from all areas
elders_health_extra <- rbind(nn_healthextra_initial, npt_healthextra_initial) %>% 
  right_join(elders_ids_linked, c("area", "home_winter_id", "adult_id_num")) %>% 
  arrange(area, adult_id_num, winter_id, sampling_visit) %>% 
  select(area, adult_id_num, adult_id_char, home, home_id_num, home_winter_id, 
         winter_id, treatment, cold2m:bronch2mdr) %>% 
  mutate_if(is_character, as_factor)

>>>>

# Load and merge files from different locations
```{r}
nn_athomelog_initial <- read_xlsx(paste0(file_path, "Input/NN/athomelog.xlsx"),
                                   na = "NULL") %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         adult_id_num = as.character(AdultID),
         area = "NN",
         sampling_visit = as.numeric(SamplingVisit),
         at_home_day = as.factor(Day),
         # making assumption participants were home during overnight hours
         "at_home_00:00:00" = as.factor("Yes"),
         "at_home_01:00:00" = as.factor("Yes"),
         "at_home_02:00:00" = as.factor("Yes"),
         "at_home_03:00:00" = as.factor("Yes"),
         "at_home_04:00:00" = as.factor("Yes"),
         "at_home_05:00:00" = as.factor("Yes"),
         "at_home_06:00:00" = as.factor("Yes"),
         "at_home_07:00:00" = as.factor(AtHome1),
         "at_home_08:00:00" = as.factor(AtHome2),
         "at_home_09:00:00" = as.factor(AtHome3),
         "at_home_10:00:00" = as.factor(AtHome4),
         "at_home_11:00:00" = as.factor(AtHome5),
         "at_home_12:00:00" = as.factor(AtHome6),
         "at_home_13:00:00" = as.factor(AtHome7),
         "at_home_14:00:00" = as.factor(AtHome8),
         "at_home_15:00:00" = as.factor(AtHome9),
         "at_home_16:00:00" = as.factor(AtHome10),
         "at_home_17:00:00" = as.factor(AtHome11),
         "at_home_18:00:00" = as.factor(AtHome12),
         "at_home_19:00:00" = as.factor(AtHome13),
         "at_home_20:00:00" = as.factor(AtHome14),
         "at_home_21:00:00" = as.factor(AtHome15),
         "at_home_22:00:00" = as.factor(AtHome16),
         "at_home_23:00:00" = as.factor("Yes")) %>% 
  select(home_winter_id:"at_home_23:00:00")

npt_athomelog_initial <- read_xlsx(paste0(file_path, "Input/NP/athomelog.xlsx"),
                                   na = "NULL") %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         adult_id_num = as.character(AdultID),
         area = "NPT",
         sampling_visit = as.numeric(SamplingVisit),
         at_home_day = as.factor(Day),
         # making assumption participants were home during overnight hours
         "at_home_00:00:00" = as.factor("Yes"),
         "at_home_01:00:00" = as.factor("Yes"),
         "at_home_02:00:00" = as.factor("Yes"),
         "at_home_03:00:00" = as.factor("Yes"),
         "at_home_04:00:00" = as.factor("Yes"),
         "at_home_05:00:00" = as.factor("Yes"),
         "at_home_06:00:00" = as.factor("Yes"),
         "at_home_07:00:00" = as.factor(AtHome1),
         "at_home_08:00:00" = as.factor(AtHome2),
         "at_home_09:00:00" = as.factor(AtHome3),
         "at_home_10:00:00" = as.factor(AtHome4),
         "at_home_11:00:00" = as.factor(AtHome5),
         "at_home_12:00:00" = as.factor(AtHome6),
         "at_home_13:00:00" = as.factor(AtHome7),
         "at_home_14:00:00" = as.factor(AtHome8),
         "at_home_15:00:00" = as.factor(AtHome9),
         "at_home_16:00:00" = as.factor(AtHome10),
         "at_home_17:00:00" = as.factor(AtHome11),
         "at_home_18:00:00" = as.factor(AtHome12),
         "at_home_19:00:00" = as.factor(AtHome13),
         "at_home_20:00:00" = as.factor(AtHome14),
         "at_home_21:00:00" = as.factor(AtHome15),
         "at_home_22:00:00" = as.factor(AtHome16),
         "at_home_23:00:00" = as.factor("Yes")) %>% 
  select(home_winter_id:"at_home_23:00:00")

@@

# Combine logs from all areas
elders_health_extra <- rbind(nn_healthextra_initial, npt_healthextra_initial) %>% 
  right_join(elders_ids_linked, c("area", "home_winter_id", "adult_id_num")) %>% 
  arrange(area, adult_id_num, winter_id, sampling_visit) %>% 
  select(area, adult_id_num, adult_id_char, home, home_id_num, home_winter_id, 
         winter_id, treatment, sampling_visit, cold2m:bronch2mdr) %>% 
  mutate(sampling_visit = as.factor(sampling_visit)) %>% 
  mutate_if(is_character, as_factor) %>% 
  filter_at(vars(cold2m:bronch2mdr), any_vars(!is.na(.))) %>% 
  distinct(area, adult_id_num, winter_id, sampling_visit, .keep_all = T)

### 2021-03-11 medvisit_data_cleaning.Rmd
data cleaning, merging cleaned datasets

---
title: "EldersAIR initial med visit data work"
author: "Ethan Walker"
date: "Started 20 Feb 2020, Updated 1 March 2021"
output: pdf_document
---

@@

elders_medvisit_clean <- elders_medvisit %>% 
  mutate_if(is_character, as_factor) %>% 
  mutate(sampling_visit = as.factor(sampling_visit)) %>% 
  mutate(stage_2_htn = if_else(bp_sys >= 140 | bp_dia >= 90, "Yes", "No"),
         stage_2_htn = as.factor(stage_2_htn),
         fev1_fvc_ratio_0.7 = if_else(fev1_fvc_ratio < 0.7, "Yes", "No"),
         fev1_fvc_ratio_0.7 = as.factor(fev1_fvc_ratio_0.7),
         spiro_grade = factor(spiro_grade, levels = c("A", "B", "C", "D", "F")),
         spiro_result = factor(spiro_result, levels = c("Normal", "Restrictive", 
                                                        "Obstructive", "Both")))

@@

#summary(elders_medvisit_clean)

>>>>

---
title: "EldersAIR initial med visit data work"
author: "Ethan Walker"
date: "Started 20 Feb 2020, Updated 11 March 2021"
output: pdf_document
---

@@

elders_medvisit_clean <- elders_medvisit %>% 
  mutate_if(is_character, as_factor) %>% 
  mutate(sampling_visit = as.factor(sampling_visit)) %>% 
  mutate(stage_2_htn = if_else(bp_sys >= 140 | bp_dia >= 90, "Yes", "No"),
         stage_2_htn = as.factor(stage_2_htn),
         fev1_fvc_ratio_0.7 = if_else(fev1_fvc_ratio < 0.7, "Yes", "No"),
         fev1_fvc_ratio_0.7 = as.factor(fev1_fvc_ratio_0.7),
         spiro_grade = factor(spiro_grade, levels = c("A", "B", "C", "D", "F")),
         spiro_result = factor(spiro_result, levels = c("Normal", "Restrictive", 
                                                        "Obstructive", "Both"))) %>% 
  # make changes based on med data file checks
  mutate(sp02 = if_else(area == "NN" & adult_id_num == 53 & winter_id == 2 & sampling_visit == 2, 
                        94, sp02),
         bp_dia = if_else(area == "NN" & adult_id_num == 47 & winter_id == 2 & sampling_visit == 1, 
                        72, bp_dia),
         bp_dia = if_else(area == "NN" & adult_id_num == 58 & winter_id == 2 & sampling_visit == 1, 
                        57, bp_dia),
         sp022 = if_else(sp02 < 90 & (pr >= 90 & pr <= 100), pr, sp02),
         pr2 = if_else(sp02 < 90 & (pr >= 90 & pr <= 100), sp02, pr)) %>% 
  select(-sp02, -pr) %>% 
  rename(sp02 = sp022,
         pr = pr2) %>% 
  replace_with_na(replace = list(sp02 = 49)) %>% 
  select(area:sampling_visit, sp02, pr, bp_sys:fev1_fvc_ratio_0.7) %>% 
  filter_at(vars(sp02:fev1_fvc_ratio_0.7), any_vars(!is.na(.))) %>% 
  distinct(area, adult_id_num, winter_id, sampling_visit, .keep_all = T)

@@

summary(elders_medvisit_clean)
